%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{amsmath}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{fontawesome}

\setlength{\textwidth}{5.1in} % Text width of the document
\usepackage{standalone}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Saoirse (née Nico) Courts} % Your name at the top
\moveleft.5\hoffset\centerline{ Communicator $\bullet$ Educator $\bullet$ Mathematician $\bullet$ Data Scientist} % Your address 

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{\faTransgenderAlt: she/they\hspace{0.3in} \faEnvelope: me@saoi.phd \hspace{0.3in} \faChain: saoi.phd \hspace{0.3in}\faLinkedinSquare: saoi-courts \hspace{0.3in}\faGithubAlt: SaoiCourts}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------

%\bigskip\moveleft.5\hoffset\centerline{
\bigskip\moveleft.5\hoffset\centerline{\it A warm and sociable mathematician and puzzle nerd with a burning desire to understand and analyze}
\moveleft.5\hoffset\centerline{\it the symptoms of---and root causes for---global conflict and injustice. My years of experience teaching}
\moveleft.5\hoffset\centerline{\it and performing research (from lit review to more creative aspects) and my compassion and empathy make}
\moveleft.5\hoffset\centerline{\it me well-suited to finding, digesting, synthesizing, and delivering instruction in complicated or esoteric}
\moveleft.5\hoffset\centerline{\it subjects. Sometimes I spend entire nights on Wikipedia binges using my custom dark mode CSS and}
\moveleft.5\hoffset\centerline{\it I wear that as a badge of honor.}

\begin{resume}

    %\section{SKILLS \&}
    %----------------------------------------------------------------------------------------
    %	PROFESSIONAL EXPERIENCE SECTION
    %----------------------------------------------------------------------------------------
    \vspace{-2.5ex}
    \section{RELEVANT EXPERIENCE}

     {\bf Postdoctoral Researcher}\hfill June 2022 -- Present\\
    Howard Hughes Medical Institute\\
    \textit{Matsen Group, Fred Hutch Cancer Center}, Seattle, WA

    \vspace{-0.1in}Used statistical and machine learning models to gain insights into how DNA mutates in B-cells to make your immune system function.

    \textbf{NSIP PhD Intern} (Machine Learning)\hfill Summer 2020 -- Summer 2021\\
    Pacific Northwest National Laboratory, Seattle, WA

    \vspace{-0.1in}Applied machine learning techniques (borrowing heavily from my mathematical background for inspiration) to solve two problems from real-world projects.

        {\bf Graduate Teaching Assistant \& Course Instructor} \hfill Sept 2016 -- June 2022 \\
    University of Washington, Seattle, WA

    \vspace{-0.1in}Taught and assisted with the instruction of math classes at all university levels, including delivering lectures and holding problem sessions.

        {\bf Lead Teaching Assistant and Instructor} \hfill Summer 2016 \\
    SCS Noonan Scholars (previously South Central Scholars), Los Angeles, CA

    \vspace{-0.1in}Independently developed and delivered Calculus II/III content for gifted students from underprivileged backgrounds.

    %\section{SELECTED PUBLICATIONS}
    %\textbf{Bundle Networks: Fiber Bundles, Local Trivializations, and a Generative Approach to Exploring Many-to-one Maps}\\
    %Nico Courts and Henry Kvinge\\
    %\textit{International Conference on Learning Representations}, 2022.

    %\textbf{Fuzzy Simplicial Networks: A Topology-Inspired Model to Improve Task Generalization in Few-shot Learning}\\
    %Henry Kvinge, Zachary New, Nico Courts, et al.\\
    %\textit{AAAI Workshop on Meta-Learning and MetaDL Challenge}, PMLR 140:77-89, 2021.

    %----------------------------------------------------------------------------------------
    %	EDUCATION SECTION
    %----------------------------------------------------------------------------------------

    \section{EDUCATION}

     {\bf Ph.D.,} Mathematics (Univ. Washington)\hfill June 2022 \\\smallskip
    {\it Representations and Support for Bosonized Quantum Complete Intersections}\\
    {\bf M.S.,} Mathematics (Univ. Washington)\hfill March 2020 \\\smallskip
    {\it Schur Duality and Strict Polynomial Functors}\\
    {\bf B.S.,} Mathematics (Univ. Southern California)\hfill May 2016\\
    {\bf A.S.,} Mathematics (Citrus College)\hfill June 2013

    \section{LEADERSHIP \\\& SERVICE}
     {\bf Team Co-Leader}\hfill September 2021\\\smallskip
    {\sl QSIDE Datathon4Justice}, Online \\
    {\bf Math Department Union Steward}\hfill Winter 2021 -- Spring 2022\\\smallskip
    {\sl UAW Local 4121 -- Postdocs \& Grad Student Union}\\
    {\bf Volunteer Judge}\hfill June 2020 \& 2021\\\smallskip
    {\sl UW Math Hour Olympiad}, Seattle, WA\\
    {\bf Graduate Student Representative}\hfill Summer 2019 -- Spring 2020\\\smallskip
    {\sl University of Washington Math Dept.}, Seattle, WA\\
    {\bf Co-organizer and Mentor}\hfill Autumn 2018 -- Spring 2021\\
    {\sl Washington Directed Reading Program}, Seattle, WA

\end{resume}
\end{document}