\documentclass[12pt]{article} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{fontawesome}
\usepackage{geometry}
\geometry{
    letterpaper,
    left=0.75in,
    right=0.75in,
    top=0.75in,
    bottom=0.75in,
}

\begin{document}
\thispagestyle{empty}

\centerline{\large\bf Saoirse (née Nico) Courts} % Your name at the top
\centerline{ Communicator $\bullet$ Educator $\bullet$ Mathematician $\bullet$ Data Scientist} % Your address
\medskip\hrule\smallskip

\centerline{\faTransgenderAlt: she/they\hspace{0.3in} \faEnvelope: me@saoi.phd \hspace{0.3in} \faChain: saoi.phd \hspace{0.3in}\faLinkedinSquare: saoi-courts \hspace{0.3in}\faGithubAlt: SaoiCourts}

\vspace{0.3in}

\noindent Nebula Hiring Team \hfill September 23, 2023\\
\\\vspace{0.2in}

\noindent To whom it may concern:\hfill\\

Thank you for taking the time to learn a little about me and why I would be a good fit as a writer on the team with Nebula.
I found this job listing because I am a Nebula subscriber (thanks RealLifeLore for hooking me in with your great videos on the Russian invasion!) to support all my favorite creators like RLL, Philosophy Tube, Second Thought, Climate Town, Not Just Bikes, and so many more!
I love that Nebula not only represents a way for creators to maintain autonomy over their videos and revenues, but also as a way to create compelling and innovative content without as much pressure on monetizability.
And for that reason, I would be ecstatic to be a part of one of the coolest media projects in the game.

I recognize that I am missing some of the formal media writing experience one would typically desire for this position, but I think that my natural affinity for language and communication---paired with my technical know-how and research and educational chops---make me an excellent addition to the team.
The majority of my writing these days falls at the far ends of the formality spectrum: ridiculously casual blog posts or formal academic writing\footnote{Examples of both can be found at my website.}, but what I believe makes me particularly apt for this position is the fact that my approach to writing is strongly informed by my training as an educator.
In particular, I value simple, direct, and meaning-rich language when communicating, rather than focusing too heavily on overly-florid prose or baroque syntax.
I am passionate about learning about the brain and intelligence in how people process and store information and about how we can deliver it in a way that is more readily absorbed; in a world flooded with data and knowledge and thousands of years of history, it is helpful to make the information that matters as digestible as possible!

As for my more human side, I am emotionally intelligent and thrive in an environment founded on collaboration and mutual benefit (and the benefit of society).
I enjoy debate and have very strongly-held convictions about some things, but also value my ability to accept when I am wrong and I always approach a disagreement with humility, empathy, and intellectual honesty in good measure.
I am a good listener and feel fulfilled when I can give someone advice or share with them a story from my life that may help them get perspective.
I'm a hugger. I'm into bouldering.

Thank you again for considering me to help you in your fascinating and, in my opinion, critical work.
I hope that you agree that the skills I have been developing over the years (admittedly in slightly different contexts!) would support that work well.

\vspace{0.25in}I hope this letter finds you well,\hfill\\\\

Saoi Courts
\end{document}