%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Nico Courts} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{University of Washington} % Your address
\moveleft.5\hoffset\centerline{Department of Mathematics}
\moveleft.5\hoffset\centerline{Box 354350}
\moveleft.5\hoffset\centerline{Seattle, WA 98195-4350}
\moveleft.5\hoffset\centerline{ncourts@uw.edu or nico@nicocourts.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS SECTION
%----------------------------------------------------------------------------------------
 
\section{RESEARCH INTERESTS}  

I am primarily interested in computation and classification of certain classes of 
Hopf algebras -- including quantum groups and Nichols algebras -- through the study of their
associated geometry, topology, and representation theory. I am studying under the direction of 
Prof. Julia Pevtsova.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

{\bf Ph.D.,} Mathematics, September 2016 -- June 2021 (expected) \\
University of Washington, Seattle, WA

{\bf Bachelor of Science,} Mathematics, May 2016 \\
{\sl Magna Cum Laude}, Phi Beta Kappa, Dean's List, Departmental Honors \\
University of Southern California, Los Angeles, CA 

{\bf Budapest Semesters in Mathematics}, Fall 2015 \\
Algebraic Topology, Conjecture \& Proof, Cryptography, Differential Geometry  \\
Budapest, Hungary 

{\bf Associates of Science,} Mathematics, June 2013\\
Key of Knowledge, Dean's list, Honors Program \\
Citrus College, Glendora, CA 
 
%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{RESEARCH EXPERIENCE}

{\sl Current Research Direction}\\
I have been studying the papers from Drinfel'd and Ginzburg \& Kumar on constructing and computing
the cohomology of the (small) quantum groups. The next step will to see how the arguments in the latter
were used by Mastnak, Pevtsova, et al to compute the cohomology of finite dimensional pointed Hopf algebras
with the hope of extending these results to even wider classes of Hopf algebras.

{\sl Graduate Reading Courses} \\
University of Washington, Seattle, WA
\begin{itemize} \itemsep -1pt % Reduce space between items
	\item Group Schemes and Algebraic Groups -- Prof. Julia Pevtsova -- {\sl Autumn 2018}
	\item Abelian Categories -- Prof. James Zhang -- {\sl Spring 2018}
	\item Representation Theory -- Prof. Julia Pevtsova -- {\sl Winter/Spring 2017}
	\item (Simplicial) Cohomology -- Prof. Steve Mitchell -- {\sl Autumn 2016}
\end{itemize}

{\sl Undergraduate Reading Courses}\\
University of Southern California, Los Angeles, CA
\begin{itemize} \itemsep -1pt % Reduce space between items
	\item {\bfseries Tools in Modern Representation Theory}. Prof. Paul Sobaje supervised as I explored topics in representations, categories, algebraic topology, module theory, Lie algebras, and support varieties. {\sl Spring 2015}
	\item {\bfseries Commutative Rings, Fields, and Galois Theory}. Under the direction of Prof. Charles Lanski, I explored topics in graduate algebra with the intent of understanding Galois theory and its applications. {\sl Fall 2014}
\end{itemize}


%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{TEACHING EXPERIENCE}

{\sl Graduate Teaching Assistant} \hfill Autumn 2016 -- Present \\
University of Washington, Seattle, WA

\begin{itemize} \itemsep -1pt % Reduce space between items
\item\textbf{As an instructor:} 
\begin{itemize}
	\item Math 124 -- Calculus I (Summer 2018)
	\item Math 308 -- Matrix Algebra (Spring 2019)
\end{itemize}
\item \textbf{As a teaching assistant:} 
\begin{itemize}
	\item Math 120 -- Precalculus (Autumn 2017)
	\item Math 124 -- Calculus I (Winter 2017, Winter 2019)
	\item Math 125 -- Calculus II (Autumn 2016, Spring 2017)
	\item Math 126 -- Calculus III (Summer 2017, Winter 2018, Spring 2018)
	\item Math 381 -- Discrete Mathematical Modeling (Autumn 2018)
\end{itemize}
\end{itemize}
 
{\sl Lead Teaching Assistant and Instructor} \hfill Summer 2016 \\
SCS Noonan Scholars (previously South Central Scholars), Los Angeles, CA
\begin{itemize} \itemsep -1pt
\item Independently developed and delivered  approximately 50 hours of instruction and five exams to gifted university-bound students in calculus 2 and 3.
\end{itemize} 

{\sl Various Teaching and Mentorship Positions} \hfill Spring 2012 -- Summer 2013 \\
Citrus College, Glendora, CA
\begin{itemize} \itemsep -1pt
\item PAGE Program Tutor
\item SIGMA Mentor
\item Math Tutor
\end{itemize} 

\section{SERVICE}

{\bf Washington Directed Reading Program}
\begin{itemize}
	\item Supervised an undergraduate student in a reading course based around Rebecca Weber's book {\sl Computability Theory} in Autumn 2018.
	\item Assisting in an administrative capacity in Spring 2019.
\end{itemize}

{\bf Math Hour Olympiad}\\
University of Washington, Seattle\\
Spring 2018\\
Volunteer Judge

{\bf Math Day}\\
University of Washington, Seattle\\
Volunteer 2017 and 2018

{\bf }

\section{\bf EVENTS ATTENDED}

{\bf ABC Workshop}\\
University of Washington, Seattle\\
November 11, 2018\\
Geometric and Cohomological Methods in Algebra

{\bf Joint Mathematical Meetings}\\
Seattle, WA\\
January 2016

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{SKILLS \& HOBBIES} 

{\sl Languages:}
\begin{itemize} \itemsep -2pt
	\item {\bfseries English} -- This is my native language.
	\item {\bfseries German} -- Ich kann ziemlich gut Deutsch sprechen, lesen, und verstehen!
	\item {\bfseries Hungarian} -- Besz\'elek csak egy kicsit magyarul.
	\item {\bfseries Programming} -- C++, C\#, {\bf Go}, {\bf Haskell}, Java, {\bf \LaTeX}, PHP, {\bf Python}.
\end{itemize}
{\sl Computer Skills:} Web/Application Development, Server Administration, Sage, Mathematica, Windows, Linux, FreeBSD.

{\sl Life Skills:} Critical Thinking, Abstract Reasoning, Communication, Objectivity, Empathy.

{\sl Hobbies:} Hiking, Jogging, Rollerskating, Appreciating the Wonders of the PNW.



\end{resume}
\end{document}